\documentclass[10pt]{article}
\usepackage{ucsdcseletterhead}
\usepackage{parskip}
\usepackage[margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{courier}
\usepackage[scaled=.92]{helvet}
\usepackage[T1]{fontenc}
\pagestyle{empty}
\begin{document}
\hfill\today

Paul Yu, Dean\\
Graduate Studies\\
402 University Center, 0003\\
UC San Diego\\
La Jolla, CA 92093-0003

\vskip\baselineskip
Dear Dean Yu,

We request permission for Sophia P. Hirakis to use the following publication
in her doctoral dissertation. Ms.\ Hirakis was the principle co-author on this paper.

 Boras, Britton W.; \textbf{\underline{Hirakis, Sophia P.}}; Votapka, Lane W.; Malmstrom, Robert D.; Amaro, Rommie E.; McCulloch, Andrew D.;"Bridging scales through multiscale modeling: a case study on protein kinase A," Fronteirs in Physiology, 6: 250, 2015.


We request permission for Sophia P. Hirakis to use the following publication in her doctoral dissertation. Ms. Hirakis is the third author of this paper.

Buffalo, Cosmo Z.; Bahn-Suh, Adrian J.; \textbf{\underline{Hirakis, Sophia P.}}; Biswas, Tapan; Amaro, Rommie E.; Nizet, Victor; Ghosh, Partho; "Conserved Patterns hidden within group A Streptococcus M protein hypervariability are responsible for recognition of human C4b-binding protein." 


We request permission for Sophia P. Hirakis to use the following publication in her doctoral dissertation. 
Ms.\ Hirakis is the principle author on this paper.

\textbf{\underline{Hirakis,}} \textbf{\underline{Sophia P.}}; Malmstrom, Robert D.; Amaro, Rommie E.; "Molecular Simulations Reveal an Unresolved Conformation of the Type IA Protein Kinase A Regulatory Subunit and Suggest its Role in the cAMP Regulatory Mechanism." The dissertation author was the primary investigator and author of this paper.


We request permission for Sophia P. Hirakis to use material currently being prepared for submission for publication. Ms. Hirakis is the principal author of  this paper.

\textbf{\underline{Hirakis, Sophia P.}};  Bartol, Thomas M.; Sejnowski, Terrence, J; Amaro, Rommie E; "title," name of journal, vol num, year. 


\vskip3\baselineskip
\parbox[t]{.5\textwidth}{%
Professor Eta Theta\\
Chair of Committee}%
\parbox[t]{.5\textwidth}{%
Laura Smith}
\end{document}
